Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-22 paper.tex
minor fixes to intro. see red comments.

@@

\title{Object Search with a Mobile Device for the Visually Impaired\\Using an Active Guidance System}

@@

\abstract{Nowadays, smartphones can be used to provide a multitude of services to assist people with visual impairments. The cameras embedded in these mobile devices, in particular, can be used for many useful tasks, including searching particular objects in unknown environments. Although previous research in computer vision has looked at ways to solve these tasks by processing the video frames of the mobile camera, very little work has been done in {\em actively} guiding the user towards specific point of interest that maximise the effectiveness of the underlying visual algorithms.
In this paper, we propose a control algorithm based on a Markov Decision Process (MDP) that generates instructions, in real-time, to guide a user searching for a target object with a smartphone's camera. The solution is part of a more general active vision application for the visually impaired. An initial implementation of the system on an Android smartphone was experimentally evaluated with sighted participants to determine the performance of the control algorithm. The results show the effectiveness of our solution and its potential application to help the visually impaired find objects in unknown environments.}

@@

\noindent It is estimated that there are 440 million people worldwide that live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives. Modern improvements to mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem. The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment with minimal user input. The proposed system implements ideas from the field of active vision, but replaces the electro-mechanical servo used in a typical control loop, pictured in Figure~\ref{fig:control-loop}, with a human. %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
  \caption{The ActVis system layout and control loop. }\label{fig:control-loop}
\end{figure}

@@

Researchers have begun implementing active search and perception~\cite{aloimonos2013active} strategies in robots and image classifiers in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.

>>>>

\newcommand{\todo}[1]{\textcolor{red}{[#1]}}

@@

\title{Active Object Search with a Mobile Device for the Visually Impaired}

@@

\abstract{Smartphones can be used to provide a multitude of services to assist people with visual impairments. The cameras embedded in these mobile devices, in particular, can be used for many useful tasks, including searching particular objects in unknown environments. Although previous research in computer vision has looked at ways to solve these tasks by processing the video frames of the mobile camera, very little work has been done in {\em actively} guiding the user towards specific point of interest that maximise the effectiveness of the underlying visual algorithms.
In this paper, we propose a control algorithm based on a Markov Decision Process (MDP) that generates instructions, in real-time, to guide a user searching for a target object with a smartphone's camera. The solution is part of a more general active vision application for the visually impaired. An initial implementation of the system on an Android smartphone was experimentally evaluated with sighted participants to determine the performance of the control algorithm. The results show the effectiveness of our solution and its potential application to help the visually impaired find objects in unknown environments.}

@@

\noindent It is estimated that almost half billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives. Modern improvements to mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
%The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or
The work here presented is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone. The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of the moving camera with the body (i.e. arm, hand) of the user holding the smartphone. Schematically, the actuators used in a typical control loop, pictured in Figure~\ref{fig:control-loop}, are replaced by a human. %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
  \caption{The ActVis system layout and control loop. \todo{Explain the meanings of the symbols r, e, ... in the caption. Remove all direct references to ActiVis with more generic ``our project''.}}\label{fig:control-loop}
\end{figure}

@@

Researchers implemented active search and perception~\cite{Bajcsy2017} strategies in robots and image classifiers in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.
